\Title

### 2016-02-14 manuscript/manuscript.tex
Caption for SAm data corrections figure

\begin{equation}
    \delta(P) = g(P) - \gamma(P).
\end{equation}

@@

\begin{equation}
    \delta_{bg}(P) = \delta(P) - g_{topo}(P).
\end{equation}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/south-america-corrections}
    \caption{Gravity data and corrections.}
    \label{fig:sam-corrections}
\end{figure*}

>>>>

\begin{equation}
    \delta(P) = g(P) - \gamma(P).
    \label{eq:disturbance}
\end{equation}

@@

\begin{equation}
    \delta_{bg}(P) = \delta(P) - g_{topo}(P).
    \label{eq:bouguer}
\end{equation}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/south-america-corrections}
    \caption{
        Gravity data for South America and the models used in the data
        corrections.
        (a) Topography from ETOPO1 sampled at $0.1^\circ$ grid spacing.
        (b) Gravitational attraction of the topography calculated
        at the observation height using tesseroids.
        (c) The gravity disturbance (Eq.~\ref{eq:disturbance}) calculated from
        the raw gravity data.
        (d) The Bouguer disturbance (Eq.~\ref{eq:bouguer}) obtained by
        subtracting (b) from (c).
        The upper (e), middle (f), and lower (g) sediment layer thicknesses
        from the CRUST1.0 model.
        (h) The total gravitational attraction of the sediment layers shown in
        (e), (f), and (g), calculated using tesseroids.
        }
    \label{fig:sam-corrections}
\end{figure*}
